master thesis

### 2018-02-17 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods - Multifurcation - Regressionsanalyse

      \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
        \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
      \#Parasiten und \#Freilebend und \#Blattknoten $\rightarrow$ Wieviele unbekannte Knoten haben wir?
      \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?
      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
        Zu der Frage, warum gibt es $nrChildren==1$. Es gibt tatsächlich 55700 Knoten mit nur einem Kind. 
          Davon ist der großteil direkt vor einem Blatt (51744), aber 3956 ($height >2$) sind irgendwo im 
          Baum. Ein paar Beispiele: \\
        Nephroselmidophyceae: (class) \\
        https://tree.opentreeoflife.org/opentree/argus/ottol@1038762 \\
        Phrynocrinidae: (family) \\
        https://tree.opentreeoflife.org/opentree/argus/ottol@3647979 \\
        Elaeocarpus sylvestris: \\
        https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969 \\
        Was bedeutet das für unsere Analyse? Ignorieren wir die \~~4000 internen und Zählen sie zu den 
          Blättern, oder zählen wir alle zu den Internen oder puzzlen wir sie einzeln raus. D.h. nur die 
          mit der Zusatzeigenschaft ($height == 2$) sind auch Blätter. \\
        Es könnte aber auch Fälle geben wie: ...-O-O-O-O-O, dann könnte man auch einen Knoten mit höherer 
          Höhe als Blatt zählen. Das müsste dann gelten $min height = max height$. \\ 
        \begin{lstlisting}
          leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
          extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
          inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
        \end{lstlisting}
        \todo{macht extendedLeaf wirklich einen Sinn?}

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Distribution of Taxa}
        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
        - The most of them are hardly represented. The major taxonomic groups are: ... \\
        - Here you can see some characteristics of the Multifurcation of the tree. \\
        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
          multipliers for some are much bigger and for others much smaller. \\
        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
          of these data. \\
        \todo{Was hierzu ist richtig und wichtig?}

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{Multifurcation}

      \begin{figure}
        \begin{subfigure}{.5\textwidth}
          \centering
          \includegraphics[width=.8\linewidth]{Figures/multifurc.pdf}
          \caption{all nodes}
        \end{subfigure}%
        \begin{subfigure}{.5\textwidth}
          \centering
          \includegraphics[width=.8\linewidth]{Figures/nr_children.pdf}
          \caption{inner nodes (shiftet to 0)}
        \end{subfigure}
        \caption{plots of children of nodes}
        \label{fig:childrenOfNodes}
        \end{figure}

      Hier Beschreibung von \ref{fig:childrenOfNodes}... \\

      \anmerkung{Description/Definition of Multifurcation $\rightarrow$ to the Intro (Bernhard)} \\
      \anmerkung{Regressionsanalyse (Bernhard)} \\
      \anmerkung{poisson glm: \#children \~ ~ I phylum $\rightarrow$ R fitdist p (Emanuel)} \\
      \anmerkung{different parameters for different taxa? (Emanuel)} \\
      One property of the tree is its ridge of multifurcation. For this we collected for every node its
        number of children (degree $-1$), and plottet this in an histogram, how much nodes we have for 
        every degree. Then we tried to find a function which best discribes this behavior. In figure 
        \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
        \todo{close(st)} to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
        $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
      \begin{figure}[h]
        \caption{Histogram of multifurcations and fitting functions}
        \centering
        \label{fig:HistogramsOfMultifurcations}
        \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
      \end{figure}
      From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
        well known and others have not been very interesting for the research so far. So we also wanted 
        to know how the multifurcations behave in some interesting subtrees. \\
      \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
      \todo{subtrees... there is some old stuff...} \\
      \todo{other subsections here...} \\

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{random binary tree}
      \anmerkung{Again, motivate first, why this is required and why you choose this solution (Bernhard)} \\
      To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
        function which returns a BaseTree \footnote{
          https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py
        }:
      \begin{lstlisting}
        from Bio import Phylo
        Phylo.BaseTree.Tree.randomized(number_leaf nodes)
      \end{lstlisting}
      From the BaseTree class:
      \anmerkung{trivial, does not give real info (Emanuel)}
      \begin{lstlisting}
        def randomized(cls, taxa, branch_length=1.0, 
              branch_stdev=None):
        """Create a randomized bifurcating tree given a list
              of taxa.
          :param taxa: Either an integer specifying the number
              of taxa to create (automatically named taxon#), 
              or an iterable of taxon names, as strings.
          :returns: a tree of the same type as this class.
        """
      \end{lstlisting}
      \todo{Zitat von BaseTree und buildTree.py}

    %---------------------------------------------------------------------------------------------------
    \subsection{tag tree}
      \anmerkung{instead of 'tag tee' simulating stages and transitions between them (Emanuel)} \\
      At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
        data.\\
      Let's say the first specie (the root node) was free-living (start with a parasite without a host 
        makes no sence). For every transition from a node to his child, we take a random number from
        the father distribution. We decided that from the biological perspective a beta distribution
        reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
      \anmerkung{why is that the case and why is that from a biological perspective? (Bernhard)} \\
      \anmerkungstext{I'd rather say that to ensure that the parameter of the binomial distribution is 
        restricted to the [0,1] interval, we model it... (Bernhard)} \\
      For example when our father node was free-living, then we take from the free-living beta
        distribution. Is the number under the threshold for beeing parasite, we get a change and tag
        the current node as parasite. Otherwise we tag it as free-living. \\
      With this procedure we traverse through the tree from the root to every leaf node. A part of
        this code you see here:
      \begin{lstlisting}
        from numpy import random
        if father_tag == 0:
          # freeliving_distribution:
          new_random = random.beta(a=A_FL, b=B_FL)
        else:
          # parasite_distribution:
          new_random = random.beta(a=A_P, b=B_P)
        tag = 0         # $\rightarrow$ FL
        if new_random < percentage_parasites:
          tag = 1       # $\rightarrow$ P
      \end{lstlisting}
      \begin{figure}
        \caption{60\% Free-living - 40\% Parasites}
        \centering
          \includegraphics[width=0.5\textwidth]{Figures/40-60.png}
      \end{figure}
      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold} \\
      We save each tag with the associated node ID in a nodelist. \\
      \anmerkung{simulationg loss of information (1) states (2) topology/multifurcation (Emanuel)} \\
      The real tree has much less information, we have only information from some current species 
        (leaf nodes) and \todo{and probably negligible internal nodes}. \\
      To simulate our real tree we save for every node an empty placeholde except for some leaf nodes.
      There we save the tags again. The amount of these unknown information is one parameter, which we
      got from our real tree. Or which we can change to \todo{...}
      \todo{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}

    %---------------------------------------------------------------------------------------------------
    \subsection{multifurcate tree}
      \anmerkung{simulating loss of information (Emanuel)} \\
      Another parameter is the nature and strength of the multifunction of the tree, since we do not 
        have a binary tree in the real case. After several measurements and analyzes, which we explain 
        in \todo{section/chapter x}, \anmerkung{fit, justification (Emanuel)} we decided to use a $\frac{1}{x}$ distribution, where x is the depth 
        of a node. This means, how deaper we are, how less information we have. \\
      We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
        as our limit ($\frac{1}{x}$), than we forget the node and hang every child to the father node of 
        the current node. \\
      \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
      \begin{lstlisting}
        from numpy import random
        from utilities import Helpers

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Taxa table}\label{sec:taxaTable2}
    \begin{center}
      % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
      \begin{tabular}{ |l|r||r|r| }
        \hline
        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes \\
        \hline \hline
        \setrow{\bfseries}kingdom & ? & - & - \\ \hline
        \setrow{\bfseries}phylum & ? & - & - \\
        superclass & 1 & 1 & 0 \\ \hline
        \setrow{\bfseries}class & 139 & 111 & 28 \\
        subclass & 82 & 72 & 10 \\
        infraclass & 8 & 7 & 1 \\
        superorder & 33 & 31 & 2 \\ \hline
        \setrow{\bfseries}order & 614 & 483 & 131 \\
        suborder & 231 & 178 & 53 \\
        infraorder & 89 & 73 & 16 \\
        parvorder & 14 & 12 & 2 \\
        superfamily & 628 & 489 & 139 \\ \hline
        \setrow{\bfseries}family & 5740 & 4202 & 1538 \\
        subfamily & 2617 & 1915 & 702 \\
        supertribe & 1 & 0 & 1 \\
        tribe & 1262 & 868 & 394 \\
        subtribe & 267 & 221 & 46 \\ \hline
        \setrow{\bfseries}genus & 127006 & 81494 & 45512 \\
        subgenus & 1176 & 801 & 375 \\ \hline
        section & 3 & 2 & 1 \\
        subsection & 1 & 1 & 0 \\
        species group + species subgroup & 181 + 93 & 129 + 74 & 52 + 19 \\
        \setrow{\bfseries}species & 1649679 & 4424 & 1645255 (1639247) \\
        subspecies & 16486 & 16 & 16470 (16449) \\
        variety + varietas & 226 + 1529 & 0 + 4 & 226 (224) + 1525 (1515) \\
        forma & 182 & 0 & 182 (182) \\
        \hline \hline
        no rank & 519 & 403 & 116 (7) \\
        no rank - terminal & 32510 & 0 & 32510 (32510) \\
        \hline  
      \end{tabular}
    \end{center}
    extended leaf nodes (real leaf nodes)

>>>>

      \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
        \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
      \#Parasiten und \#Freilebend und \#Blattknoten $\rightarrow$ Wieviele unbekannte Knoten haben wir?
      \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?
      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
        Zu der Frage, warum gibt es $nrChildren==1$. Es gibt tatsächlich 55700 Knoten mit nur einem Kind. 
          Davon ist der großteil direkt vor einem Blatt (51744), aber 3956 ($height >2$) sind irgendwo im 
          Baum. Ein paar Beispiele: \\
        Nephroselmidophyceae: (class) \\
        https://tree.opentreeoflife.org/opentree/argus/ottol@1038762 \\
        Phrynocrinidae: (family) \\
        https://tree.opentreeoflife.org/opentree/argus/ottol@3647979 \\
        Elaeocarpus sylvestris: \\
        https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969 \\
        Was bedeutet das für unsere Analyse? Ignorieren wir die $\sim$ 4000 internen und Zählen sie zu den 
          Blättern, oder zählen wir alle zu den Internen oder puzzlen wir sie einzeln raus. D.h. nur die 
          mit der Zusatzeigenschaft ($height == 2$) sind auch Blätter. \\
        Es könnte aber auch Fälle geben wie: ...-O-O-O-O-O, dann könnte man auch einen Knoten mit höherer 
          Höhe als Blatt zählen. Das müsste dann gelten $min height = max height$. \\ 
        \begin{lstlisting}[gobble=8]
          leaf.taxa <-  all.taxa[all.taxa$nr_children==0, ]
          extendedLeaf.taxa <- all.taxa[all.taxa$nr_children<2 & min.height==max.height, ]
          inner.taxa <- all.taxa[all.taxa$nr_children>1 | (all.taxa$nr_children==1 & min.height!=max.height), ]
        \end{lstlisting}
        \todo{macht extendedLeaf wirklich einen Sinn?}

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Distribution of Taxa}
        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
        - The most of them are hardly represented. The major taxonomic groups are: ... \\
        - Here you can see some characteristics of the Multifurcation of the tree. \\
        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
          \ref{fig:taxaTable2}. \\
        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
          of these data. \\
        \todo{Was hierzu ist richtig und wichtig?}
        \begin{figure}
          \centering
          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
          \caption{Distribution of Nodes in Rank-Cathegories}
          \label{fig:taxaTable2}
        \end{figure}

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{Multifurcation}
      Ein von den Daten beeinflusster Parameter ist die Multifurkation des Baumes, d.h. wie weit sind 
        wir von einem binären Baum entfehrnt, was hängt mit der stärke der Multifurkation zusammen und 
        welche Auswirkung hat sie auf unsere Fragestellung. \\
      In Figure \ref{fig:childrenOfNodes} haben wir die Multifurkation über den gesamten Baum abgebildet,
        dazu haben wir für jeden Knoten die Anzahl seiner Kinder gezählt und dies als Histogram 
        geplottet. \\
      Subfigure \ref{fig:childrenOfNodes_innerNodes} beschränkt sich hierbei nur auf die inner nodes 
        während Subfigure \ref{fig:childrenOfNodes_allNodes} alle Knoten abbildet. \\
      \todo{Welchen der beiden Plots wollen wir nehmen, einer genügt eigentlich.}

      \begin{figure}
        \begin{subfigure}{.5\textwidth}
          \centering
          \includegraphics[width=.8\linewidth]{Figures/multifurc.pdf}
          \caption{all nodes}
          \label{fig:childrenOfNodes_allNodes}
        \end{subfigure}%
        \begin{subfigure}{.5\textwidth}
          \centering
          \includegraphics[width=.8\linewidth]{Figures/nr_children.pdf}
          \caption{inner nodes (shiftet to 0)}
          \label{fig:childrenOfNodes_innerNodes}
        \end{subfigure}
        \caption{plots of children of nodes}
        \label{fig:childrenOfNodes}
      \end{figure}

      Wir haben verschiedene Eigenschaften der Multifurkation untersucht:
      \begin{itemize}
        \item stärke der Multifurcation in verschiedenen Subbäumen
        \item zusammenhang zur tiefe im Baum
        \item zusammenhang zu höhe im baum
        \item einfluss auf die vorhersage des Castor und Fitch Algorithmus (Simulation) \todo{...}
      \end{itemize}

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Poisson regression}

        \begin{lstlisting}[gobble=8]
          glm(formula = multifurc ~ 1, family = "poisson", data = inner.taxa)
        \end{lstlisting}
        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
        (Intercept: Stärke der Multifurcation) \\
        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
        Chloroplastida than in Metazoa:
        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
          des Baums mit dem folgenden Deviance Table:

        \begin{center}
          \begin{tabular}{ |l|r|l| }
            \hline
            Model & Residuals Dev & Deviance Pr(>Chi) \\
            \hline \hline
            multifurc $\sim$ kingdom & 7774454 & \\
            multifurc $\sim$ phylum & 7435700 & 338754 \\
            multifurc $\sim$ class & 7337241 & 98459 \\
            \rowcolor{green} multifurc $\sim$ order & 7076068 & 261172 \\

            % [1] "------------------------kingdom - phylum - class - order--------------------------"
            % Analysis of Deviance Table

            % Model 1: multifurc ~ kingdom
            % Model 2: multifurc ~ phylum
            % Model 3: multifurc ~ class
            % Model 4: multifurc ~ order
            %   Resid. Df Resid. Dev  Df Deviance  Pr(>Chi)
            % 1    167222    7774454
            % 2    167173    7435700  49   338754 < 2.2e-16 ***
            % 3    167039    7337241 134    98459 < 2.2e-16 ***
            % 4    166352    7076068 687   261172 < 2.2e-16 ***
            % ---
            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

            % 1] "-------------------phylum - depth / min/max/mean.height-----------------------"
            % Analysis of Deviance Table

            % Model 1: multifurc ~ phylum
            % Model 2: multifurc ~ phylum + depth
            % Model 3: multifurc ~ phylum + min.height
            % Model 4: multifurc ~ phylum + max.height
            % Model 5: multifurc ~ phylum + mean.height
            %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
            % 1    167173    7435700
            % 2    167172    7431609  1     4090 < 2.2e-16 ***
            % 3    167172    7233486  0   198124
            % 4    167172    7375889  0  -142403
            % 5    167172    7128318  0   247570
            % ---
            % Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
            % [1] "--------------------------------------------------"

            \hline \hline
            multifurc $\sim$ order & 4762407 & \\
            multifurc $\sim$ order + max.height & 4721600 & $40807 < 2.2e-16$ \\
            \rowcolor{green} multifurc $\sim$ order * max.height & 4674368 & $47233 < 2.2e-16$ \\
            \hline
            multifurc $\sim$ order & 4762407 & \\
            multifurc $\sim$ order + min.height & 4712672 & $49735 < 2.2e-16$ \\
            multifurc $\sim$ order * min.height & 4694783 & $17889 < 2.2e-16$ \\
            \hline
            multifurc $\sim$ order & 4762407 & \\
            multifurc $\sim$ order + mean.height & 4717014 & $45393 < 2.2e-16$ \\
            multifurc $\sim$ order * mean.height & 4694424 & $22590 < 2.2e-16$ \\
            \hline \hline
            multifurc $\sim$ phylum & 4664706 & \\
            multifurc $\sim$ phylum + max.height & 4601257 & 63449 < 2.2e-16 \\
            \rowcolor{green} multifurc $\sim$ phylum * max.height & 4546220 & 55036 < 2.2e-16 \\
            \hline \hline
            multifurc $\sim$ class & 4581569 & \\
            multifurc $\sim$ class + max.height & 4510567 & 71003 \\
            \rowcolor{green} multifurc $\sim$ class * max.height & 4434635 & 75932 \\

          \end{tabular}
        \end{center}
        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün)\\
        * Deviance - Abweichung

      \anmerkung{different parameters for different taxa? (Emanuel)} \\
      One property of the tree is its ridge of multifurcation. For this we collected for every node its
        number of children (degree $-1$), and plottet this in an histogram, how much nodes we have for 
        every degree. Then we tried to find a function which best discribes this behavior. In figure 
        \ref{fig:HistogramsOfMultifurcations} is this plot shown with three functions, which came 
        closest to this goal: $\frac{1000000000000000}{x^4}$ (magenta), 
        $\frac{300000000000}{x^3}$ (red) and $\frac{80000000}{x^2}$ (black). \\
      \begin{figure}[h]
        \caption{Histogram of multifurcations and fitting functions}
        \centering
        \label{fig:HistogramsOfMultifurcations}
        \includegraphics[width=0.7\textwidth]{Figures/HistogramsOfMultifurcations.png}
      \end{figure}
      From the biology we know, that this multifurcation is very clouded. Some parts of the tree are 
        well known and others have not been very interesting for the research so far. So we also wanted 
        to know how the multifurcations behave in some interesting subtrees. \\
      \anmerkung{do we? Is that really universal knowledge or could it be supported by data or a citation? (Bernhard)} \\
      \todo{subtrees... there is some old stuff...} \\
      \todo{other subsections here...} \\

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{random binary tree}
      \anmerkung{Again, motivate first, why this is required and why you choose this solution (Bernhard)} \\
      To get a random binary tree, I used the Phylo package from biopython. They offer a randomized
        function which returns a BaseTree \footnote{
          https://github.com/biopython/biopython/blob/master/Bio/Phylo/BaseTree.py
        }:
      \begin{lstlisting}[gobble=6]
        from Bio import Phylo
        Phylo.BaseTree.Tree.randomized(number_leaf nodes)
      \end{lstlisting}
      From the BaseTree class:
      \anmerkung{trivial, does not give real info (Emanuel)}
      \begin{lstlisting}[gobble=6]
        def randomized(cls, taxa, branch_length=1.0, 
              branch_stdev=None):
        """Create a randomized bifurcating tree given a list
              of taxa.
          :param taxa: Either an integer specifying the number
              of taxa to create (automatically named taxon#), 
              or an iterable of taxon names, as strings.
          :returns: a tree of the same type as this class.
        """
      \end{lstlisting}
      \todo{Zitat von BaseTree und buildTree.py}

    %---------------------------------------------------------------------------------------------------
    \subsection{tag tree}
      \anmerkung{instead of 'tag tee' simulating stages and transitions between them (Emanuel)} \\
      At this point we want one fully tagged tree, and one less tagged tree which looks like our real 
        data.\\
      Let's say the first specie (the root node) was free-living (start with a parasite without a host 
        makes no sence). For every transition from a node to his child, we take a random number from
        the father distribution. We decided that from the biological perspective a beta distribution
        reflects our transition probabilities best (see Figure 2.1 \todo{ref einfügen}). \\
      \anmerkung{why is that the case and why is that from a biological perspective? (Bernhard)} \\
      \anmerkungstext{I'd rather say that to ensure that the parameter of the binomial distribution is 
        restricted to the [0,1] interval, we model it... (Bernhard)} \\
      For example when our father node was free-living, then we take from the free-living beta
        distribution. Is the number under the threshold for beeing parasite, we get a change and tag
        the current node as parasite. Otherwise we tag it as free-living. \\
      With this procedure we traverse through the tree from the root to every leaf node. A part of
        this code you see here:
      \begin{lstlisting}[gobble=6]
        from numpy import random
        if father_tag == 0:
          # freeliving_distribution:
          new_random = random.beta(a=A_FL, b=B_FL)
        else:
          # parasite_distribution:
          new_random = random.beta(a=A_P, b=B_P)
        tag = 0         # $\rightarrow$ FL
        if new_random < percentage_parasites:
          tag = 1       # $\rightarrow$ P
      \end{lstlisting}
      \begin{figure}
        \caption{60\% Free-living - 40\% Parasites}
        \centering
          \includegraphics[width=0.5\textwidth]{Figures/40-60.png}
      \end{figure}
      \todo{Bessere Beschriftung, Plot neu erstellen! U.a. mit threshold} \\
      We save each tag with the associated node ID in a nodelist. \\
      \anmerkung{simulationg loss of information (1) states (2) topology/multifurcation (Emanuel)} \\
      The real tree has much less information, we have only information from some current species 
        (leaf nodes) and \todo{and probably negligible internal nodes}. \\
      To simulate our real tree we save for every node an empty placeholde except for some leaf nodes.
      There we save the tags again. The amount of these unknown information is one parameter, which we
      got from our real tree. Or which we can change to \todo{...}
      \todo{Was hiervon gehört ind Methoden, was schon in Implementierung oder ganz woanders hin?}

    %---------------------------------------------------------------------------------------------------
    \subsection{multifurcate tree}
      \anmerkung{simulating loss of information (Emanuel)} \\
      Another parameter is the nature and strength of the multifunction of the tree, since we do not 
        have a binary tree in the real case. After several measurements and analyzes, which we explain 
        in \todo{section/chapter x}, \anmerkung{fit, justification (Emanuel)} we decided to use a $\frac{1}{x}$ distribution, where x is the depth 
        of a node. This means, how deaper we are, how less information we have. \\
      We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
        as our limit ($\frac{1}{x}$), than we forget the node and hang every child to the father node of 
        the current node. \\
      \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
      \begin{lstlisting}[gobble=6]
        from numpy import random
        from utilities import Helpers

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Taxa table}\label{sec:taxaTable2}
    \begin{center}
      % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
      \begin{tabular}{ |l|r||r|r|r| }
        \hline
        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes & Terminal Leaf Nodes \\
        \hline \hline
        \setrow{\bfseries}domain & 1 & 1 & &  \\ \hline
        \setrow{\bfseries}kingdom & 3 & 3 & &  \\
        subkingdom & 2 & 2 & & \\
        infrakingdom & 5 & 5 & & \\
        superphylum & 2 & 2 & & \\ \hline
        \setrow{\bfseries}phylum & 57 & 54 & 3 & \\
        subphylum & 22 & 20 & 2 & \\
        infraphylum & 2 & 2 & & \\
        superclass & 8 & 8 & & \\ \hline
        \setrow{\bfseries}class & 209 & 175 & 34 & \\
        subclass & 120 & 106 & 14 & \\
        infraclass & 14 & 11 & 3 & \\
        superorder & 40 & 37 & 3 & \\ \hline
        \setrow{\bfseries}order & 1014 & 772 & 242 & \\
        suborder & 285 & 222 & 63 & \\
        infraorder & 95 & 78 & 17 & \\
        parvorder & 14 & 12 & 2 & \\
        superfamily & 829 & 626 & 203 & \\ \hline
        \setrow{\bfseries}family & 8449 & 6143 & 2306 & \\
        subfamily & 3090 & 2250 & 840 & \\
        supertribe & 1 & 0 & 1 & \\
        tribe & 1764 & 1285 & 479 & \\
        subtribe & 435 & 359 & 77 & \\ \hline
        \setrow{\bfseries}genus & 164656 & 105452 & 59204 & \\
        subgenus & 1266 & 869 & 397 & \\
        section & 3 & 2 & 1 & \\
        subsection & 1 & 1 & 0 & \\
        species group & 365 & 288 & 77 & \\
        species subgroup & 123 & 100 & 23 & \\ \hline
        \setrow{\bfseries}species & 2247251 & 7423 & 2239828 & 2228993 \\
        subspecies & 22437 & 75 & 22362 & 22239 \\
        variety & 1755 & 7 & 1748 & 1726 \\
        varietas & 5970 & 19 & 5951 & 5909 \\
        forma & 1181 & & 1181 & 1181 \\
        \hline \hline
        no rank & 954 & 719 & 235 & 7 \\
        no rank - terminal & 37452 & & 37452 & 37452 \\
        (no entry) & 40099 & 40099 & & \\
        \hline  
      \end{tabular}
    \end{center}
    extended leaf nodes (real leaf nodes)
